% Based on template #1 from https://www.overleaf.com/project/66b0e99eef0dfa4776e66478

\documentclass[11pt]{article} 

%\usepackage{times} % uncomment for Times Roman;
\usepackage{bm} % If you want bold math, but without the bloat of AMS packages
\usepackage{color} % doh
\usepackage{hyperref} % LaTeX cross references become hyperlinks in pdf output
\usepackage{graphicx} % For figure insertion
\usepackage{vmargin} % To set page size

% Set up bibliography: https://www.overleaf.com/learn/latex/Bibliography_management_in_LaTeX
\usepackage[backend=biber]{biblatex}
\addbibresource{../references.bib}


\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\setpapersize{USletter}
\setmarginsrb{1in}{1in}{1in}{1in}{0pt}{0mm}{0pt}{0mm}

\newcommand{\pseudodot}{{\lower 2.4pt\hbox{$\cdot$}}} % to avoid tripping URL scanners: e.g. Data\pseudodot{}gov ('Data.gov')

\begin{document}
\pagestyle{empty} 
\setlength{\baselineskip}{12.6pt} 


\section{Introduction\label{sec:intro}}
Context/Need/Gap/Hero Funnel. \cite{matthis_retinal_2022}


\subsection{Intellectual Merit\label{sec:IM}}
How we will advance knowledge 


\section{Broader Impacts\label{sec:BI}}
How we will help the world

\section{Objectives}
 Like Specific Aims - what are the primary activities/deliverables?

\newpage

\section{Current Context}
\subsection{Technological Context}
\subsection{Social Context}
\subsection{Ethical Context}
\subsubsection{The Problem of Universities}
\subsubsection{The Problem of Journals}
\subsubsection{On Gardens and Cottage Industries}
\subsection{Need and Gap}

\section{Objectives and Long term vision}
\subsection{Aspirational Goals}
\subsubsection{FreeMoCap => Best MoCap}
\subsubsection{All-levels accessible}
\subsubsection{Covert Education}
\subsubsection{Generative Organzational Structure}


\section{Guiding Principles}
\subsection{Universal Design / Universal Access}
\subsection{No artificial scarcity}
\subsection{Community Focus}
\subsection{Aggressively Open Source}

\section{The FreeMoCap Project (FMC)}
\subsection{Artifacts}

\subsubsection{FreeMoCap Softwares}
\paragraph{FreeMoCap Core Software (FMC-Core)}
\paragraph{Sub-Skelly Softwares}

\subsubsection{Documentation and Educational Material}

\subsubsection{Datasets and derived models}


\subsection{The FreeMoCap Community (FMC-C)}

\subsection{The FreeMoCap Foundation (FMC-F)}
\subsubsection{Organization}
\subsubsection{Governance}
\subsubsection{Responsibilities}
\subsubsection{Licensing Model}

\section{Planned Activitites and Objectives}

\subsection{Ecosustem establishment and growth}
\subsubsection{Userbase Analysis/Engagement}
\subsubsection{AI Psuedo-Mentorship (SkellyBot)}

\subsection{Community Building}
\subsubsection{Annual Workshop/Conference: FreeMoCamp/Con}
\subsubsection{Community Challenges}
\subsubsection{Community Grants Program}
\subsubsection{Gamification and acheivement-based badges}

\subsection{Organization and Governance}
\subsubsection{Build admin infrastrcutre}
\subsubsection{Develop SOPs}
\subsubsection{Establish core maintainer roles and support}
\subsubsection{Develop 'Skelly Enhancement Proposal'[SEP] system}

\subsection{Continuous Development, integration, Evaluation}
\subsubsection{Development}
\subsubsection{Integration}
\subsubsection{Evaluation}
\paragraph{Tests.}
\paragraph{Validation.}
\paragraph{Diagnostics.}

\subsection{Sustainability}
\subsubsection{Goals and Metrics}
\paragraph{Community Growth.}
\paragraph{Organizational Stability.}
\paragraph{Software Performance.}
\paragraph{Revenue streams.}

\subsection{Security and Privacy}
\subsection{Security}
\subsection{Privacy}

\newpage
\printbibliography
\end{document}